### 2019-12-06 frontmatter.tex
Modified reference style.

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	This thesis deals with high energy super-lasers. A brief introduction on the
	basic concepts and methods is presented in the first part. The second part
	contains two articles.
	The papers are adjusted to comply with the present thesis format for
	consistency, but their contents have not been altered as compared with their
	original counterparts.
\end{preface}

>>>>

%-------------------------------------------------------------------------------
% Preface page
%-------------------------------------------------------------------------------
%
\begin{preface}
	\change{This thesis deals with high energy super-lasers. A brief introduction on the
	basic concepts and methods is presented in the first part. The second part
	contains two articles.
	The papers are adjusted to comply with the present thesis format for
	consistency, but their contents have not been altered as compared with their
	original counterparts.}
\end{preface}
